The Spatial and Temporal Domains of Modern Ecology

### 2017-12-22 paper/main.tex
Redid sensitivity analysis vignette in full

\noindent \textbf{\emph{Differences between actual and ostensible scales}}\\
For our final analysis of observational domains, we evaluated the differences between the scales represented by the extent and duration dimensions and the scales that ecological observations actually cover. To make this assessment, we log$_{10}$ transformed and then subtracted the values of i) actual extent from extent and ii) actual duration from duration, yielding the magnitude of difference between each pair of dimensions for each observation. We plotted these values (summarized in box plots) against their corresponding extent/duration values to evaluate whether these differences varied with scale (Fig. 3). Extent was on average 5.6 orders of magnitude larger than actual extent, and this difference increased with extent, reaching a maximum of 8 orders of magnitude between 100 million and 1 billion ha of extent (Fig. 3A). The difference fell to 3 orders of magnitude at 10 billion ha, a domain that was covered by the $<$2\% of observations that were primarily collected with remote sensing. Remote observations had the smallest mean difference magnitude (1.9), compared to 5.7 or larger for the other three methods (see Fig. S3 in SI for method-specific plots).

>>>>

\noindent \textbf{\emph{Differences between actual and ostensible scales}}\\
For our final analysis of observational domains, we evaluated the differences between the scales represented by the extent and duration dimensions and the scales that ecological observations actually cover. To make this assessment, we log$_{10}$ transformed and then subtracted the values of i) actual extent from extent and ii) actual duration from duration, yielding the magnitude of difference between each pair of dimensions for each observation. We plotted these values (summarized in box plots) against their corresponding extent/duration values to evaluate whether these differences varied with scale (Fig. 3). Extent was on average 5.6 orders of magnitude larger than actual extent, and this difference increased with extent, reaching a maximum of 8.3 orders of magnitude between 100 million and 1 billion ha of extent (Fig. 3A). The difference fell to 3 orders of magnitude between 1-10 billion ha, a domain that was covered by the $<$2\% of observations that were primarily collected with remote sensing. Remote observations had the smallest mean difference magnitude (1.9), compared to 5.7 or larger for the other three methods (see Fig. S3 in SI for method-specific plots).
